---
title: "Assignment 4"
author: "Your Name Here"
date: "`r format(Sys.time(), '%d %h, %Y, %I:%M %p')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions:

1. Update your name in the header block, example: `author: "Alex Fout" `
1. Select `File > Save as` and save the file by adding your last name at the beginning with an underscore, example: `fout_assignment_4.rmd`
1. Follow the instructions below to fill in the assignment.
1. Be sure to _run your code chunks when you make them_, to make sure everything works!
1. When you've completed the assignment, __knit__ the document and make sure the resulting HTML or PDF file looks alright.
1. Upload the PDF or HTML file to Canvas (Don't upload the Rmd document).


# Assignment

This assignment will give you practice creating visualizations in R, using data on the market value of soccer players (footballers) in 2021. 
If you have a Kaggle account, you can download the data here: [https://www.kaggle.com/sanjeetsinghnaik/most-expensive-footballers-2021/version/1], but we provide it for you at [https://github.com/CSU-R/Module2/blob/master/data_raw/players.csv] as well so you can download it without a Kaggle account.

## Problem 1. 

Load the players.csv dataset into a dataframe called `pl`.
Since we will be using the fifth column (`Markey.Value.In.Millions.Â..`) quite a lot, rename it to just "Value".


```{r}
# your code here
```


## Problem 2.

Using `base` `R` graphics, create a scatter plot with `Age` on the X axis and `Value` on the Y axis.
Make the points a filled circle (search for "pch" options online) colored blue (using the `col` command).
Give the plot a suitable title.
What do you observe for older players?

```{r}
# your code here
```

## Problem 3

Now create a boxplot in `base` `R` graphics using the `boxplot` function, showing a boxplot for player value, grouped by player position.
(hint: try ?boxplot, and under "Arguments", look for how the formula should be formatted; Some of the examples may help as well).
Make your boxplot horizontal by adding the "horizontal=T" argument, and rotate the y axis labels with the "las=1" argument.
Then decrease the size of the y labels using "cex.axis=0.5".
Give the plot a suitable title.
The thick bar in the middle of the bar is the Median for the group. Which position appears to have the lowest median value?

```{r}
# your code here
```

## Problem 4

Make one more plot in `base` `R`, showing the Value vs. Matches. Then set the color based on whether a player's value is greater than 80, by setting the color command equal to `value>80`. You may have to convert it to a factor as well.

```{r}
# your code here
```

## Problem 5

Now you'll create some graphics in `ggplot2`.
First, recreate the plot of Value vs. Age, again using blue points (hint: since the color of each point doesn't depend on the data, you won't define an aesthetic for color; instead, set the "color" argument within geom_point() to be "blue").
Add a title by __adding__ the "labs" function with the argument "title" set to "Value vs. Age".
Change the theme of the plot by adding the `theme_classic` theme, similar to how `theme_bw` is added in the textbook.

```{r}
# Your code here
```

## Problem 6

Now create a boxplot with Position on the X axis and Value on the Y axis. 
Instead of the `geom_point()` function, you'll be using `geom_boxplot()`.
Set the theme to `theme_bw()`, and give the plot an appropriate title.
Also, add the following command, which will make the group labels more readable: `theme(axis.text.x = element_text(angle=45, hjust=1))`


```{r}
# Your code here
```

## Problem 7

Now copy and paste your code from problem 6 below, and change the `geom_boxplot()` to 
Set the theme to `theme_bw()`, and use the `scale_color_distiller` function with the "YlGn" palette to color the points by the `Matches` variable. You will also have to add `Matches` as an aesthetic in the `ggplot` function.
Note: `scale_color_distiller` is like `scale_color_brewer`, but the former is for coloring continuous variables, and the latter is for coloring categorical variables.

```{r}
# Your code here
```

## Problem 8

Finally, you'll use `ggplotly` to make a more interactive graphic.
Make a scatter plot with Goals on the x axis and Value on the Y axis, and color by Matches.
Add two more labels in the aesthetics including `Name` and `Club`, so they can be included in the plotly tooltip.
Give the plot an appropriate title.
Use `scale_color_distiller` with the "Reds" palette, and be sure to set `direction=1`, so the color scale gets larger for more Matches.

Now use the `ggplotly` function to display the plot, with the tooltip including `Name`, `Club`, `Value`, and `Matches`.


```{r}
# Your code here
```

## End

This is the end of the assignment!
You can knit the document and upload it to Canvas

