---
title: "Assignment 2"
author: "Your Name Here"
date: "`r format(Sys.time(), '%d %h, %Y, %I:%M %p')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions:

1. Update your name in the header block, example: `author: "Alex Fout" `
1. Select `File > Save as` and save the file by adding your last name at the beginning with an underscore, example: `fout_assignment_2.rmd`
1. Follow the instructions below to fill in the assignment.
1. Be sure to _run your code chunks when you make them_, to make sure everything works!
1. When you've completed the assignment, __knit__ the document and make sure the resulting HTML or PDF file looks alright.
1. Upload the PDF or HTML file to Canvas (Don't upload the Rmd document).


# Assignment

This assignment will give you some experience scraping data from the web, as well as some data cleaning with `tidyverse` functions.

## Problem 1. 

The website [j-archive.com] contains a near-complete compendium of jeopardy clues, responses, contestants, winners, wagers, and much more! 
For this problem, you'll scrape some data from a few games. 

For this first problem, navigate to the website and notice under the site logo are numbers for every season of the show. Pick a season and click on its number, where you'll see a list of games. Pick a game and click on the link to navigate to that game's page. 

Now use `rvest` to read the html from the game you chose. Make sure you get the correct url by checking your browser's address bar, there should be a game_id referenced in the url.
Assign this html to a variable called `site`.


```{r}
require(rvest)
require(dplyr)
# your code here
```

## Problem 2

Now extract the contents of the top-left clue of the game board using the `html_node` function on the `site` variable, specifying the `css` to be "#clue_J_1_1". This will extract the correct cell of the clue table. 
Then _pipe_ the result using `%>%` to the `html_text()` function to extract the clue text, similar to the example in the textbook.
print the text of the clue you extracted.

```{r}
# your code here
```

## Problem 4

Now use the SelectorGadget or your browser's inspect feature to identify the name of the table class for the "Jeopardy!" (the top table) and "Double Jeopardy!" (the bottom table) rounds.
When you select the correct element of the webpage, you should see the table grid hightlighted.
Use `rvest` to read the entire table from the `site` variable specifying the class you found as the `css` argument.
Assign the answer to a variable called `clues`.

```{r}
# your code here
```


## Problem 5

In this problem you'll work with a dataset scraped from Wikipedia about Academy Award Nominated/Winning films.
The code to scrape the compile the list of films is already written for you, The result is a 3 column data frame called films

```{r}
# code to retrieve the list of oscar nominated films
require(dplyr)
require(tidyr)
tables <- read_html("https://en.wikipedia.org/wiki/Academy_Award_for_Best_Picture") %>%
  html_nodes(css=".wikitable") %>% html_table()
tables[[length(tables)]] <- NULL
tables <- lapply(tables, function(table){names(table) <- c("Year", "Film", "Studio/Producers"); table})
films <- do.call(rbind, tables)
head(films)
```

Run the code above to construct the films data frame.
Becuase of the way the data were formatted, there are extra rows with `NA` in them.
Use the filter function to filter out the rows where the `Film` column is `NA` (hint, use the `is.na` function) and assign the result to a variable called films2

```{r}
# your code here
```

### Problem 6

The winning film is the first one listed in each year.
Extract the winning films by grouping `films2` by the `Year` column and then using the `slice_head` function to extract the first row from each group.
Assign the result to a variable named `winners`

```{r}
# your code here
```


### Problem 7

Determine how many films were nominated each year by grouping by the `Year` column and using the summarize function. 
Hint, the `n()` function counts how many rows are in each group, so you can try something like `nominated=n()` inside summarize.

```{r}
# your code here
```

Use this data frame to answer the question: What was the first year after 1950 with more than 5 nominees?

Answer: 


## End

This is the end of the assignment!
You can knit the document and upload it to Canvas

